## Example 6

Set working directory


Read in homework6 data

```{r}
dat<-read.csv("homework6.csv")
```
Load libraries

```{r}
library(ggplot2)
library(gplots)
library(dplyr)
```


The fabricated data are supposed to approximate how people perform
in different types of visual searches. Specifically, we're 
comparing performance in feature searches (e.g. looking for a red
X among green Xs) and conjunction searches (e.g. looking for a red
X among green Xs and red Os). We're also looking at how the number
of distractors within the search display effect our data.
-->
 
 Check the structure of the data

```{r}
str(dat)
```

Change any variables that should be factor variables into factor variables.
```{r}
dat$type<-as.factor(dat$type)
dat$subject<-as.factor(dat$subject)
dat$subject2<-as.factor(dat$subject2)
```

Perform a one-way between-subjects ANOVA examining for the effects of the number of distractors for the conjunction searches only.

 Data from conjunction searches only
 
```{r}
temp<-dat[dat$distractor=="yes",]
```

Run ANOVA
```{r}
summary(aov(rt~type, data=temp))
```


```{r}
library(ggplot2)
library(gplots)
library(dplyr)

                
```


Create line graph

```{r}
temp<-temp%>%group_by(type)%>%
  summarize(means=mean(rt),
            sems=sd(rt)/sqrt(length(type)))

f<-ggplot(temp, aes(x=as.factor(type),
                    y=means,
                    group=1))+
  geom_line(size=1)+
  geom_point(size=2)+
  geom_errorbar(aes(ymax=means+sems,
                    ymin=means-sems),
                width=.2)+
  ggtitle("Serial Type Effect")+
  labs(x="List Position",y="Percent Recalled")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())
f

                
```

<!--
Perform a one-way between-subjects ANOVA examining for effects of 
the the number of distractors for the conjunction searches only.
Also create a line graph to help you interpret the results of your
analysis.
-->
Distractors only.

```{r}


temp<-dat[dat$distractor=="yes",]
 


                
```



Perform a one-way within subjects ANOVA on the same data you analyzed


```{r}
temp<-dat[dat$distractor=="yes",]
```

Perform a between-subjects ANOVA examining for the effects of and interactions between the number of distractors and the search type.

```{r}
summary(aov(rt~type*distractor, data=dat))
```


Summarizing data in preparation of creating a bar graph.

```{r}
temp<-dat%>%group_by(type,distractor)%>%
  summarize(means=mean(rt),
            sems=sd(rt)/sqrt(length(n)))
```
Creating the figures

```{r}
f<-ggplot(temp, aes(x=position,
                    y=means,
                    group=distractor,
                    color=distractor))+
  geom_line(size=1)+
  geom_point(size=2)+
  scale_color_manual(values=c("darkgreen","red"),
                     name="Distractor",
                     breaks=c("no","yes"),
                     labels=c("No", "Yes"))+
  geom_errorbar(aes(ymax=means+sems, ymin=means-sems),width=.2)+
  ggtitle("Serial Position With and Without Distraction")+
  labs(x="List Position",y="Percent Recalled")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())+
  theme(legend.position=c(.4,.76))+
  theme(legend.background=element_blank())+
  theme(legend.background=element_rect(color="black"))+
  theme(legend.title=element_blank())+
  theme(legend.title=element_text(size=12))+
  theme(legend.title.align=.5)+
  theme(legend.text=element_text(size=10,face="bold"))
f

f<-ggplot(temp, aes(x=position,
                    y=means,
                    fill=distractor))+
  geom_bar(stat="identity",position=position_dodge())+
  scale_fill_manual(values=c("darkgreen","red"),
                     name="Distractor",
                     breaks=c("no","yes"),
                     labels=c("No", "Yes"))+
  geom_errorbar(aes(ymax=means+sems,
                    ymin=means-sems),
                width=.2,
                position=position_dodge(.9))+
  ggtitle("Serial Position With and Without Distraction")+
  labs(x="List Position",y="Percent Recalled")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())+
  theme(legend.position=c(.4,.76))+
  theme(legend.background=element_blank())+
  theme(legend.background=element_rect(color="black"))+
  theme(legend.title=element_blank())+
  theme(legend.title=element_text(size=12))+
  theme(legend.title.align=.5)+
  theme(legend.text=element_text(size=10,face="bold"))
f
```


Perform a within-subjects two-way ANOVA examining for the effects
of and interactions between number of distractors and search type.
Tip: use subject as the subject's variable for this analysis.


```{r}
summary(aov(percent~type*distractor+
              Error(subject/(type*distractor)),
                    data=dat))
```

Finally conduct and interpret the results of a mixed ANOVA in which
number of distractors varies within subjects and the type of search
varies between subjects. 

```{r}
summary(aov(percent~type*distractor+
              Error(subject2/type),
            data=dat))
```
