---
title: "vlammey"
output: html_document
---



Read in the homework5.csv data and set working directory.


```{r}
dat<-read.csv("data5.csv")
```


Check the structure of the data

```{r}
str(dat)

```

Find the mean words per minute for the two groups
```{r}
mean(dat$support[dat$wpm=="none"])
mean(dat$support[dat$wpm=="metal"])

```

Run an independent t-test to determine if the mean wpm for the
no music group is different from the mean wpm from heavy metal
group.

```{r}
t.test(df$rt[df$group=="none"],
       df$rt[df$group=="metal"],
       var.equal=TRUE)
```

Run another independent t-test with the alternative hypothesis that
the heavy metal group types faster than the no music group. 

```{r}
t.test(dat$rt[dat$group=="none"],
       dat$rt[dat$group=="metal"],
       var.equal=TRUE,
       alternative="greater")

```

Load libraries


```{r}
library(ggplot2)
library(gplots)
library(dplyr)
install.packages("ggplot2")
install.packages("gplots")
install.packages("dplyr")

```


```{r}
library(ggplot2)
library(gplots)
library(dplyr)

temp<-dat%>%group_by(group)%>%
  summarize(means=mean(rt), sems=sd(rt)/sqrt(length(rt)))


```

```



Create a bar graph of the data.

```{r}
f<-ggplot(temp,aes(x=factor(group),y=means))+
  geom_bar(stat="identity", color="black",
           fill=c("deepskyblue2", "deeppink"))+
  geom_errorbar(aes(ymax=means+sems,
                    ymin=means-sems),
                width=.2)+
  ggtitle("Graph")+
  labs(x="Group", y="Response Time (ms)")+
  scale_x_discrete(breaks=c("control","experimental"),
                   labels=c("Control","Experimental"))+
  theme(plot.title=element_text(size=15,
                                face="bold",
                                vjust=.5))+
  theme(axis.title.x=element_text(size=12,
                                  face="bold",
                                  vjust=-.25))+
  theme(axis.title.y=element_text(size=12,
                                  face="bold",
                                  vjust=.25))+
  theme(axis.text.x=element_text(size=10,
                                 face="bold",
                                 color="black"))+
  theme(axis.text.y=element_text(size=10,
                                 face="bold",
                                 color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),
        axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())
f
```

Conduct and interpret a two-tailed paired t-test on the data.

```{r}
t.test(dat$rt[dat$group=="none"],
       dat$rt[dat$group=="metal"],
       var.equal=TRUE,
       paired=TRUE)
```

